Lens Recovery with GLASS: An Extensible Free-Form Gravitational Lens Modeling Framework

### 2013-02-19 limits/ms.tex
Mostly restructuring of the order of sections.

@@

\title{Limits on constraining galaxy profiles with current and future strong gravitational lensing}
\author{%
Jonathan Coles 
\and 
Justin Read
\and 
Prasenjit Saha 
}

@@

\begin{abstract}
We show the effectiveness of reconstructing the mass distribution of four mock galaxies using
a range of strong gravitational lensing assumptions. In particular, we study
the affects of the lens morphology (double or quad) with and without a central
image, angular image distribution, and red shift contrast between two sources.
The lens modeling is performed using a new free-form framework called \Glass.
We conclude that 
1) Time delays are unnecessary with strong red shift contrast,
2)

@@

To date only about 100 strong lenses are known, but within the next ten years
new surveys will discover thousands of gravitational lenses. For example, SKA
in 2020 estimates about 10,000 lenses and the LSST in 2022 expects to find
about 5,000 multiply-imaged galaxies and about 150 AGNs or quasar lenses.

@@

The lensing equation
%
\begin{equation}
\vec\beta = \vec\theta - \frac{D_{LS}}{D_S}\vec\alpha(\vec\theta)
\label{lensing equation}
\end{equation}
%
maps an observed image position $\vec\theta$ to a source position $\vec\beta$
via the correction factor 
%
\begin{equation}
\vec\alpha(\vec\theta) = \frac{4G}{c^2} \int \Sigma(\vec\theta')\frac{(\vec\theta - \vec\theta')}{\ |\vec\theta - \vec\theta'|^2}d^2\vec\theta'
\end{equation}
%
which accounts for the gravitational lensing effect of an intervening mass. For
our purposes we make use of the thin mass sheet approximation and assume that
the lensing mass is infinitely thin compared with the distance between the
source and the lens $D_{LS}$ and the lens and the observer $D_{L}$. These
distances are angular diameter distances where $D_* = (c/H_0)d_*$ and $d_*$ is
a dimensionless number that depends on cosmology.  The lens can then be thought
of as a projected surface density $\Sigma$ which diverts the path of a photon
instantaneously through the bending angle $\vec\alpha$.

@@

If we think of $\tau$ as a surface then images will be observed where ever
$\nabla \tau = 0$. In other words, images obey Fermat's principle and appear at
extremums of the surface. Note that $\nabla \tau$ is just \eqnref{lensing equation}.

@@

The steepness degeneracy arbitrarily rescales the arrival time surface. Image
positions are left alone but the density profile will become shallower or
steeper. This is particularly bad for inferring the Hubble constant, as the
lens profile will tend to become steeper for larger values of $H_0$.

Other degeneracies include ring degeneracies, where one is allowed to build
up a density distribution as a series of mass rings; the presence of substructure;
and the effects of merging galaxies.

Shape degeneracy---a twisting in the density.

@@

\Glass\ is an evolution of the concepts employed by the free form modeling tool
\PixeLens\ but completely rewritten in Python and C. The key improvements are:
\begin{enumerate}
  \item A modular framework allows new priors to be added and modified easily;
  \item The basis functions approximating a model can be changed; 
  \item Non-linear constraints can be imposed in an automated post-processing step; 
  \item The central region can be have a higher resolution to capture steep models; 
  \item Stellar density can be used as an additional constraint.  
  \item Point or extended mass objects in the field.
\end{enumerate}
At its heart lies a new algorithm for sampling high dimensional linear spaces
that is used to generate lensing models. This algorithm was described and
tested in \cite{}. \Glass\ is also multi-threaded allowing it to run
efficiently on many-cored machines.  The software is freely available for
download. In our tests we will take advantage of each of these new features.

@@

For this paper we will restrict ourselves to using the pixelated basis set that
has been employed in previous work and is implemented in \PixeLens. Here we will
briefly review the main ideas. The algorithm for generating models in \Glass\
samples a convex polytope in a high dimensional space whose interior points are
solutions to the lensing equation and satisfy other physically motivated linear
priors. We must therefore formulate all of our equations as equations linear in the
unknowns. We describe the density distribution
$\kappa$ as a set of discrete grid cells or pixels $\kappa_i$.
In this way, we rewrite the potential (\eqnref{lensing potential}) as
%
\begin{equation}
  \psi(\vec\theta) = \sum_n \kappa_n Q_n(\vec\theta)
\end{equation}
%
where the sum runs over all the pixels and $Q_n$ is the integral of the logarithm
over pixel $n$. The exact form for $Q$ is described in \appref{Q derivation}.
The pixels only cover a finite circular area with physical radius $\Rmap$ and 
pixel radius $\Rpix$. To account for any global shearing outside this region
from, e.g., a neighboring galaxy, we also add two shearing terms
%
\begin{equation}
\gamma_1(\theta_x^2 - \theta_y^2) + 2\gamma_2\theta_x\theta_y\quad.
\end{equation}
%
We can continue adding terms to account for assumed potentials or potentials
induced from the presence of other galaxy in the field. If the stellar density
has been estimated we can use this as a lower bound where the stellar potential
is a known constant
%
\begin{equation}
  \psi^*(\vec\theta) = \sum_n \kappa^*_n Q_n(\vec\theta)\quad.
\end{equation}
%
We can find the discretized lens equation by simply taking the gradient of the
above equations.

The solution space constrained by the lens equation and the arrival times are
not enough to form a closed volume. We have not imposed any strong constraints
on the density even so much as to ensure that it is non-negative everywhere. We
must therefore provide additonal linear constraints so that we generate physical
models. The explicit implementation for these priors has been explained in. In
summary, we require that
\begin{enumerate}
\item The density must be non-negative everywhere.
\item The density profile must have a slope everywhere $\le 0$. This prevents hollow rings.
\item The local gradient everywhere must point within $45^{\circ}$ of the center.
\item Density variations must be smooth.
\item Image parity is enforced.
\item The density is radially symmetric. (Optional)
\end{enumerate}

In the simplest form a single model for a lens is a tuple of the form
$\M = (\vec\kappa, \beta, \gamma_1, \gamma_2)$. A single model represents a 
single point in the solution space polytope. Using the MCMC sampling strategy
described in \cite{} we uniformly sample this space. Collectively, the sampled
models are referred to as an ensemble $\E = \{\M_i\}$, where we typically
generate 1000 models. We will typically show the ensemble average $|\E|$ in the
plots to follow.

@@

\subsection{Raytracing}
\Glass\ can also determine the position of images and time delays from 
particle-based simulation output given a source position $\vec\beta$. This is
used to generate the lens configurations used in the parameter study.  The
particles are first projected onto a very high resolution grid representing the
lens plane. The centers of each of the grid cells are mapped back onto the
source plane using \eqnref{lensing equation}. If the location on the source
plane is within a user specified $\eps_\mathrm{accept}$ of $\vec\beta$ then the
point on the image plane is accepted and further refined using a root finding
algorithm until the distance to $\vec\beta$ is nearly zero. If multiple points
converge to an $\eps_\mathrm{root}$ of each other then only one point is taken.
Care must be taken that the grid resolution is high enough that the resulting
image position error is below the equivalent observational error. Time delays
are the calculated in order from the arrival time at each image (\eqnref{tau}).

@@

The four mock galaxies we consider have been designed to test our 
recovery procedure on galaxies that have steep and shallow dark matter
and stellar profiles. The enclosed mass in all cases is fixed at $M(a_\star)=
0.18\e{11}$ at the scale radius $a_\star=2$ kpc. These values were chosen to
closely resemble B1115. We therefore also place the galaxy at a redshift of
$z_L = 0.31$. Throughout, we assume a cosmology where $H_0^{-1}=13.7$ Gyr, $\Omega_M=0.28$,
and $\Omega_\Lambda=0.72$.

@@

\begin{table}
\begin{tabular}{clllllll}
Galaxy & $\gamma_\star$ & $M_\star$ & $\gamma_\mathrm{DM}$ & $M_\mathrm{DM}$ \\
\hline
AA & 1 & 4 & 0.05 & $11^{2.95}$ \\
AC & 1 & 4 & 1 & $11^2$ \\
BB & 1.5 & $2^{1.5}$ & 0.16 & $11^{2.84}$ \\
BC & 1.5 & $2^{1.5}$ & 1 & $11^2$
\end{tabular}
\caption{Profile parameters for the four mock galaxies. The resulting profiles only roughly follow
\eqnref{Dehnen profile} because the galaxies are triaxial. Masses are in units of $0.18\e{11}\Msun$. The scale lengths for
all lenses are $(a_\star,a_\mathrm{DM})=(2,20)$ kpc and by definition
$M_\star(a_\star) = M_\mathrm{DM}(a_\star) = 1$.}
\label{Lens profile params}
\end{table}

In \figref{mock galaxies} we show the 3D radial density, 
the 2D projected density, and the 2D enclosed mass for each
galaxy. Solid lines represent the total mass, dashed lines the dark 
matter, and dotted lines the stellar mass. The projected plot has
been normalized to the critical density 
$\kappa_\mathrm{crit}\sim 1.8\e{9}$.

@@

\subsection{Test scenarios} %--------------------------------------------------------------

For each galaxy we constructed ten test scenarios:
\begin{enumerate}
\item Two double imaged systems with a single point source,
\item Two quadruply imaged systems with a single point source,
\item One extended source, 
\item A two-source system with one source varying across five redshifts. 
%will provide a robust estimate of the enclosed mass at
%several radii, suggesting that given a large enough separation, redshift
%constrast will provide the most robust constraint on the mass profile of a
%halo.
\end{enumerate}

%\tabref{Test configurations} summarizes how each of the configurations is composed.  
\figref{Test reconstructions} shows the reconstructed lens.

\begin{figure}
\plotone{AAarrival_surfaces}
\plotone{BBarrival_surfaces}
\plotone{BCarrival_surfaces}
\caption{Average reconstructions of each test case assuming time delays and no central image
using (from \textbf{top} to \textbf{bottom}) the galaxies AA, (AC MISSING), BB, BC.}
\label{Test reconstructions}
\end{figure}

\subsection{Recovery} %--------------------------------------------------------------

\begin{table}
\begin{tabular}{lccccc}
Source name & $z$ & $\beta$ & Image & $\vec\theta$ & $\Delta t$ (days) \\
\hline
AASingleSourceR1a & 1.72 & -0.59, 0.10 & A & -2.64, 5.07 & \\
 & & & B & -3.15, -4.62 & 37.09\\
 & & & C & -5.72, -0.67 & 33.58\\
 & & & D & 4.26, -0.20 & 259.75\\
 & & & E & 0.22, -0.02 & 104.48\\
AASingleSourceR1b & 1.72 & 0.11, -0.46 & A & 0.49, -5.85 & \\
 & & & B & 0.87, 4.91 & 228.69\\
 & & & C & 4.80, 1.57 & 31.83\\
 & & & D & -4.58, 1.40 & 56.15\\
 & & & E & -0.09, 0.11 & 180.09\\
AAExtendedSourceR1a & 1.72 & -0.23, -0.13 & A & -1.08, -5.48 & \\
 & & & B & -1.26, 5.19 & 66.27\\
 & & & C & -5.31, 0.49 & 74.72\\
 & & & D & 4.72, 0.33 & 99.26\\
 & & & E & 0.04, 0.02 & 174.11\\
AAExtendedSourceR1b & 1.72 & -0.37, 0.04 & A & -1.73, 5.27 & \\
 & & & B & -1.93, -5.13 & 14.76\\
 & & & C & -5.53, -0.27 & 75.45\\
 & & & D & 4.56, -0.05 & 160.47\\
 & & & E & 0.09, -0.01 & 147.24\\
AAExtendedSourceR1c & 1.72 & -0.62, -0.13 & A & -2.84, -5.01 & \\
 & & & B & -3.47, 4.36 & 60.96\\
 & & & C & -5.66, 0.92 & 17.14\\
 & & & D & 4.13, 0.23 & 270.45\\
 & & & E & 0.40, 0.06 & 83.81\\
AASingleSourceR2 & 1.50 & 0.11, -0.46 & A & 0.49, -5.66 & \\
 & & & B & 0.98, 4.67 & 227.84\\
 & & & C & 4.48, 1.70 & 27.39\\
 & & & D & -4.34, 1.34 & 54.57\\
 & & & E & -0.12, 0.21 & 144.98\\
AASingleSourceR3 & 1.00 & 0.11, -0.46 & A & 0.48, -5.05 & \\
 & & & B & 0.92, 3.98 & 226.30\\
 & & & C & 3.70, 1.67 & 19.74\\
 & & & D & -3.55, 1.20 & 53.34\\
 & & & E & -0.12, 0.15 & 96.33\\
AASingleSourceR4 & 0.80 & 0.11, -0.46 & A & 0.39, -4.50 & \\
 & & & B & 0.93, 3.38 & 223.14\\
 & & & C & 2.98, 1.69 & 9.75\\
 & & & D & -2.82, 1.09 & 48.86\\
 & & & E & -0.15, 0.18 & 52.90\\
AASingleSourceR5 & 0.72 & 0.11, -0.46 & A & 0.44, -4.22 & \\
 & & & B & 1.02, 2.94 & 219.75\\
 & & & C & 2.51, 1.69 & 4.63\\
 & & & D & -2.36, 1.03 & 44.24\\
 & & & E & -0.16, 0.20 & 32.56
\end{tabular}
\end{table}

\subsection{With/without time delays and central image} %--------------------------------------------------------------

We also considered the effect of having time delays or a central image. The
central image is usually highly demagnified and obscured by the lensing galaxy,
but in clusters the central image is observable. In this case we can imagine
the galaxies to be clusters since the problem is scale-free. A recontruction of
AASingleQuadR1a\_Tm is shown in \figref{AASingleQuadR1a_Tm}. The suffix denotes
which combination of time delays (T) and central image (M) was used. An
uppercase letter indicates the feature is turned on, and a lowercase letter
that it is turned off.

\begin{figure}
%\plotone{AASingleQuadR1a_Tm.png}
\caption{The reconstruction of AASingleQuadR1a\_Tm.}
\end{figure}

@@

\subsection{Model quality}
We estimate of the quality of a model $\M_i$ by comparing the recovered
density profile $\rho_\M(r)$ against the profile of the mock galaxy $\rho_G(r)$.
In particular, the plots show the RMS quantity
%
\begin{equation}
  \chi_i = 100 \times \sqrt{\frac{\int_r (\rho_{\M_i}(r) - \rho_G(r))^2}{\int_r \rho_G(r)^2}}
  %\chi_i = \frac{\sum_r (\rho(r)_{\M_i} - \rho(r)_G)^2}{\sum_r \rho(r)_G^2}
\end{equation}

\begin{figure}
\plotone{AAZContrastR1R5_Tm.pdf}
\caption{A typical reconstructed lens. The first panel on the left shows the
arrival time surface. In this case, there are two sources at different
redshifts with galaxy AA. The next three panels show the radial density,
average enclosed density, and enclosed mass profiles, respectively.  The grey
curve is from the galaxy and the vertical lines show the positions of the
images for the two sources.}
\end{figure}

\begin{figure}
\label{chi2}
\plottwo{AAchi2_profile.pdf}{AAchi2_profile.pdf} \\
\plottwo{BBchi2_profile.pdf}{BCchi2_profile.pdf}
\caption{
Goodness of fit plots for the reconstruction of each of the four galaxies given
the different lensing test cases. The $\chi^2$ is computed over the radial $\kappa$
profile with data points at the median value and the error bars showing the 68\% confidence
interval.
}
\end{figure}

@@

\section{Stellar mass}
\begin{itemize}
\item Assume perfect knowledge of the stellar mass distribution.
\item Construct a lens system where the images are probing the stellar region.
\item Add stellar mass as a minimum constraint on the pixels.
\item Requires more pixels in the middle to correctly and efficiently be resolved
\item Stellar mass improves the reconstruction. Need to explain how.
\end{itemize}

@@

\section{Velocity dispersions}
\begin{itemize}
\item Can they predict radial profiles?
\item Can we constrain lensing models from predicted velocity dispersions?
\item Use a constructed spherical halo G2 following a $\rho \propto r^{-\gamma}$ profile with stellar halo same as G1.
\item Vary $z$ of the halo, possibly orientation.
\item Should be able to recover $\gamma$ very well.
\item Use G1. Show problems with recovering $\gamma$.
\end{itemize}

\section{PCA of the models to uncover degeneracies}

@@

\section{GLASS - An Extensible Gravitational Lens Modeling Framework}
\label{GLASS Description}
\begin{itemize} 
\item Framework that incorporates lens modeling, analysis, and plotting.
\item Not limited to just pixels based modeling. Can be used with functional forms like Bessel functions. Not yet implemented.
\item Allows for post processing and criteria matching on a per model basis.
\item Input files are python programs but from within the framework that aspect may be ignored.

\item Lens reconstruction. Based on PixeLens. Express data constraints and
priors as linear equations. Sample the resulting simplex.
\item Standard data constraints: image positions, time delays, hubble constant, parity, annular density, external shear.
\item Priors: range of profile steepness, local gradient, smoothness, shared H0, symmetry for doubles.
\item Local gradient and smoothness are now convergent. Based on physical size rather than number of neighbors.

\item Raytracing. Use a fine grid to sample the 2d function mapping position on
the image plane to distance from the source on the source plane. From those
points that are near the source, use a 2d root finder to locate the exact
positions. Merge nearly identical solutions.

\end{itemize}

>>>>

\newcommand{\Eavg}{\ensuremath{\langle \E \rangle}}

@@

%\title{Limits on constraining galaxy profiles with current and future strong gravitational lensing}
\title[GLASS]{Lens Recovery with GLASS: An Extensible Free-Form Gravitational Lens Modeling Framework}
\author{%
Jonathan P. Coles 
\and 
Justin I. Read
\and 
Prasenjit Saha 
}

@@

\begin{abstract}
We show the effectiveness of reconstructing the mass distribution of four mock galaxies using
a range of strong gravitational lensing assumptions. In particular, we study
the affects of the lens morphology (double or quad) with and without a central
image, angular image distribution, and red shift contrast between two sources.
The lens modeling is performed using a new free-form framework called \Glass.
We conclude that \dots
%1) Time delays are unnecessary with strong red shift contrast,
%2)

@@

To date only about 400 strong lenses are known, but within the next ten years
new surveys will discover thousands of gravitational lenses. The SKA estimates
that after its start in 2020 about 10,000 lenses will be found. The LSST
expects to find about 5,000 multiply-imaged galaxies and about 150 AGNs or
quasar lenses after 2022.

@@

The lensing equation
%
\begin{equation}
\vec\beta = \vec\theta - \frac{D_{LS}}{D_S}\vec\alpha(\vec\theta)
\label{lensing equation}
\end{equation}
%
maps an observed image position $\vec\theta$ to a source position $\vec\beta$
via the correction factor 
%
\begin{equation}
\vec\alpha(\vec\theta) = \frac{4GD_L}{c^2} \int \Sigma(\vec\theta')\frac{(\vec\theta - \vec\theta')}{\ |\vec\theta - \vec\theta'|^2}d^2\vec\theta'
\end{equation}
%
which accounts for the gravitational lensing effect of an intervening mass. For
our purposes we make use of the thin mass sheet approximation and assume that
the lensing mass is infinitely thin compared with the distance between the
source and the lens $D_{LS}$ and the lens and the observer $D_{L}$. These
distances are angular diameter distances where $D_* = (c/H_0)d_*$ and $d_*$ is
a dimensionless number that depends on cosmology.  The lens can then be thought
of as a projected surface density $\Sigma$ which diverts the path of a photon
instantaneously through the bending angle $\vec\alpha$.

@@

If we think of $\tau$ as a surface then images will be observed where ever
$\nabla \tau = 0$. In other words, images obey Fermat's principle and appear at
extremums of the surface. Note that $\nabla \tau$ is just \eqnref{lensing equation} or
\begin{equation}
  \xi \vec\beta = \xi \vec\theta - \frac 1\pi\int \kappa_\infty\frac{(\vec\theta - \vec\theta')}{\ |\vec\theta - \vec\theta'|^2}d^2\vec\theta'
\end{equation}

@@

\begin{itemize}
  \item Steepness
  \item Shape
  \item $H_0$
  \item Rings
  \item Cosmology
\end{itemize}

%
%The steepness degeneracy arbitrarily rescales the arrival time surface. Image
%positions are left alone but the density profile will become shallower or
%steeper. This is particularly bad for inferring the Hubble constant, as the
%lens profile will tend to become steeper for larger values of $H_0$.
%
%Other degeneracies include ring degeneracies, where one is allowed to build
%up a density distribution as a series of mass rings; the presence of substructure;
%and the effects of merging galaxies. 
%
%Shape degeneracy---a twisting in the density.

@@

\Glass\ is an evolution of the concepts employed by the free form modeling tool
\PixeLens\ but completely rewritten in Python and C. The key improvements are:
\begin{enumerate}
  \item A modular framework allows new priors to be added and modified easily.
  \item The basis functions approximating a model can be changed. 
  \item Non-linear constraints can be imposed in an automated post-processing step. 
  \item The central region can be have a higher resolution to capture steep models. 
  \item Stellar density can be used as an additional constraint.  
  \item Point or extended mass objects can be placed in the field.
\end{enumerate}
In our tests we will take advantage of each of these new features.  At its
heart lies a new algorithm for sampling high dimensional linear spaces that is
used to generate lensing models. This algorithm was described and tested in
\cite{}. \Glass\ is also multi-threaded allowing it to run efficiently on
many-cored machines.  The software is freely available for download. One
interesting aspect is that the input files are themselves Python programs. This
allows a large amount of sophistication in setting up a lens at runtime and
also allows \Glass\ to be used as an external library from another user written
program.

@@

For this paper we will restrict ourselves to using the pixelated basis set that
has been employed in previous work and is implemented in \PixeLens. Here we will
briefly review the main ideas. The algorithm for generating models in \Glass\
samples a convex polytope in a high dimensional space whose interior points are
solutions to the lensing equation and satisfy other physically motivated linear
priors. We must therefore formulate all of our equations as equations linear in the
unknowns. We describe the density distribution
$\kappa$ as a set of discrete grid cells or pixels $\kappa_i$.
In this way, we rewrite the potential (\eqnref{lensing potential}) as
%
\begin{equation}
  \psi(\vec\theta) = \sum_n \kappa_n Q_n(\vec\theta)
  \label{discrete potential}
\end{equation}
%
where the sum runs over all the pixels and $Q_n$ is the integral of the logarithm
over pixel $n$. The exact form for $Q$ is described in \appref{Q derivation}.
We can find the discretized lens equation by simply taking the gradient of the
above equations.

The pixels only cover a finite circular area with physical radius $\Rmap$ and 
pixel radius $\Rpix$. To account for any global shearing outside this region
from, e.g., a neighboring galaxy, we also add two shearing terms
%
\begin{equation}
\gamma_1(\theta_x^2 - \theta_y^2) + 2\gamma_2\theta_x\theta_y\quad.
\end{equation}
%
We can continue adding terms to account for assumed potentials or potentials
induced from the presence of other galaxy in the field. If the stellar density
has been estimated we can use this as a lower bound where the stellar potential
is a known constant of the form \eqnref{discrete potential}.
%
%\begin{equation}
  %\psi^*(\vec\theta) = \sum_n \kappa^*_n Q_n(\vec\theta)\quad.
%\end{equation}
%

Unfortunately, the lens equation and the arrival times are not enough to form a
closed volume in the solution space. We have not imposed any strong constraints
on the density even so much as to ensure that it is non-negative everywhere. We
must therefore provide additonal linear constraints so that we generate
physical models. The explicit implementation for these priors has been
explained in \cite{}. In summary, we require that
\begin{enumerate}
\item The density must be non-negative everywhere.
\item The density profile must have a slope everywhere $\le 0$. This prevents hollow rings.
\item The local gradient everywhere must point within $45^{\circ}$ of the center.
\item Density variations must be smooth.
\item Image parity is enforced.
\item The density is radially symmetric. (Optional)
\end{enumerate}

In the simplest form, a single model for a lens is a tuple $\M = (\vec\kappa,
\beta, \gamma_1, \gamma_2)$. A single model represents a single point in the
solution space polytope. Using the MCMC sampling strategy described in \cite{}
we uniformly sample this space. Collectively, the sampled models are referred
to as an ensemble $\E = \{\M_i\}$, where we usually generate $\sim$1000 models. We
will typically show the ensemble average $\Eavg$ in the plots to
follow.

@@

\subsection{Raytracing}
\label{Raytracing}
\Glass\ can also determine the position of images and time delays from 
particle-based simulation output given a source position $\vec\beta$. This is
used to generate the lens configurations used in the parameter study.  The
particles are first projected onto a very high resolution grid representing the
lens plane. The centers of each of the grid cells are mapped back onto the
source plane using \eqnref{lensing equation}. If the location on the source
plane is within a user specified $\eps_\mathrm{accept}$ of $\vec\beta$ then the
point on the image plane is accepted and further refined using a root finding
algorithm until the distance to $\vec\beta$ is nearly zero. If multiple points
converge to an $\eps_\mathrm{root}$ of each other then only one point is taken.
Care must be taken that the grid resolution is high enough that the resulting
image position error is below the equivalent observational error. Time delays
are the calculated in order from the arrival time at each image (\eqnref{tau}).

@@

The four mock galaxies we consider have been designed to test our recovery
procedure on galaxies that have steep and shallow dark matter and stellar
profiles. The enclosed mass in all cases is fixed at $M(a_\star)= 0.18\e{11}$
at the scale radius $a_\star=2$ kpc. These values were chosen to closely
resemble B1115. We therefore place the galaxy at a redshift of $z_L = 0.31$.
Throughout, we assume a cosmology where $H_0^{-1}=13.7$ Gyr, $\Omega_M=0.28$,
and $\Omega_\Lambda=0.72$. The critical density is $\kappa_\mathrm{crit}\sim
1.8\e{9}$\Msun/kpc$^2$.

@@

\begin{table}
\begin{tabular}{cllllllll}
Galaxy & $\gamma_\star$ & $M_\star$ & $\gamma_\mathrm{DM}$ & $M_\mathrm{DM}$ & Notes\\
\hline
AA & 1 & 4 & 0.05 & $11^{2.95}$ & \\
AC & 1 & 4 & 1 & $11^2$ & \\
BB & 1.5 & $2^{1.5}$ & 0.16 & $11^{2.84}$ & \\
BC & 1.5 & $2^{1.5}$ & 1 & $11^2$ & 
\end{tabular}
\caption{Profile parameters for the four mock galaxies. The resulting profiles only roughly follow
\eqnref{Dehnen profile} because the galaxies are triaxial. Masses are in units of $0.18\e{11}\Msun$. The scale lengths for
all lenses are $(a_\star,a_\mathrm{DM})=(2,20)$ kpc and by definition
$M_\star(a_\star) = M_\mathrm{DM}(a_\star) = 1$.}
\label{Lens profile params}
\end{table}

@@

In \figref{mock galaxies} we show the 3D radial density, 
the 2D projected density, and the 2D enclosed mass for each
galaxy. Solid lines represent the total mass, dashed lines the dark 
matter, and dotted lines the stellar mass. The projected plot has
been normalized to the critical density.

\subsection{Lens configurations} %--------------------------------------------------------------

For each of the four galaxies, we used the raytracing feature of \Glass\
described in \secref{Raytracing} to construct 12 lensing scenarios:

\begin{enumerate}
\item Two double imaged systems with a single point source.
\item Two quadruply imaged systems with a small and large annulus.
\item Two quadruply imaged systems with a single point source.
\item One extended source. 
\item A two-source quad system with one source varying across five redshifts. 
\end{enumerate}

Each of these configurations were modeled with and without time delays and with
and without a central image. We assumed for all tests that the lensing mass was
symmetric.

\subsection{Stellar mass}
\begin{itemize}
\item Assume perfect knowledge of the stellar mass distribution.
\item Construct a lens system where the images are probing the stellar region.
\item Add stellar mass as a minimum constraint on the pixels.
\item Requires more pixels in the middle to correctly and efficiently be resolved
\item Stellar mass improves the reconstruction. Need to explain how.
\end{itemize}

\subsection{Velocity dispersions}

\begin{itemize}
\item Can they predict radial profiles?
\item Can we constrain lensing models from predicted velocity dispersions?
\item Use a constructed spherical halo G2 following a $\rho \propto r^{-\gamma}$ profile with stellar halo same as G1.
\item Vary $z$ of the halo, possibly orientation.
\item Should be able to recover $\gamma$ very well.
\item Use G1. Show problems with recovering $\gamma$.
\end{itemize}

%\tabref{Test configurations} summarizes how each of the configurations is composed.  
%\figref{Test reconstructions} shows the reconstructed lens.

%\begin{figure}
%\plotone{AAarrival_surfaces}
%\plotone{BBarrival_surfaces}
%\plotone{BCarrival_surfaces}
%\caption{Average reconstructions of each test case assuming time delays and no central image
%using (from \textbf{top} to \textbf{bottom}) the galaxies AA, (AC MISSING), BB, BC.}
%\label{Test reconstructions}
%\end{figure}

%\subsection{Recovery} %--------------------------------------------------------------

%\begin{table}
%\begin{tabular}{lccccc}
%Source name & $z$ & $\beta$ & Image & $\vec\theta$ & $\Delta t$ (days) \\
%\hline
%AASingleSourceR1a & 1.72 & -0.59, 0.10 & A & -2.64, 5.07 & \\
% & & & B & -3.15, -4.62 & 37.09\\
% & & & C & -5.72, -0.67 & 33.58\\
% & & & D & 4.26, -0.20 & 259.75\\
% & & & E & 0.22, -0.02 & 104.48\\
%AASingleSourceR1b & 1.72 & 0.11, -0.46 & A & 0.49, -5.85 & \\
% & & & B & 0.87, 4.91 & 228.69\\
% & & & C & 4.80, 1.57 & 31.83\\
% & & & D & -4.58, 1.40 & 56.15\\
% & & & E & -0.09, 0.11 & 180.09\\
%AAExtendedSourceR1a & 1.72 & -0.23, -0.13 & A & -1.08, -5.48 & \\
% & & & B & -1.26, 5.19 & 66.27\\
% & & & C & -5.31, 0.49 & 74.72\\
% & & & D & 4.72, 0.33 & 99.26\\
% & & & E & 0.04, 0.02 & 174.11\\
%AAExtendedSourceR1b & 1.72 & -0.37, 0.04 & A & -1.73, 5.27 & \\
% & & & B & -1.93, -5.13 & 14.76\\
% & & & C & -5.53, -0.27 & 75.45\\
% & & & D & 4.56, -0.05 & 160.47\\
% & & & E & 0.09, -0.01 & 147.24\\
%AAExtendedSourceR1c & 1.72 & -0.62, -0.13 & A & -2.84, -5.01 & \\
% & & & B & -3.47, 4.36 & 60.96\\
% & & & C & -5.66, 0.92 & 17.14\\
% & & & D & 4.13, 0.23 & 270.45\\
% & & & E & 0.40, 0.06 & 83.81\\
%AASingleSourceR2 & 1.50 & 0.11, -0.46 & A & 0.49, -5.66 & \\
% & & & B & 0.98, 4.67 & 227.84\\
% & & & C & 4.48, 1.70 & 27.39\\
% & & & D & -4.34, 1.34 & 54.57\\
% & & & E & -0.12, 0.21 & 144.98\\
%AASingleSourceR3 & 1.00 & 0.11, -0.46 & A & 0.48, -5.05 & \\
% & & & B & 0.92, 3.98 & 226.30\\
% & & & C & 3.70, 1.67 & 19.74\\
% & & & D & -3.55, 1.20 & 53.34\\
% & & & E & -0.12, 0.15 & 96.33\\
%AASingleSourceR4 & 0.80 & 0.11, -0.46 & A & 0.39, -4.50 & \\
% & & & B & 0.93, 3.38 & 223.14\\
% & & & C & 2.98, 1.69 & 9.75\\
% & & & D & -2.82, 1.09 & 48.86\\
% & & & E & -0.15, 0.18 & 52.90\\
%AASingleSourceR5 & 0.72 & 0.11, -0.46 & A & 0.44, -4.22 & \\
% & & & B & 1.02, 2.94 & 219.75\\
% & & & C & 2.51, 1.69 & 4.63\\
% & & & D & -2.36, 1.03 & 44.24\\
% & & & E & -0.16, 0.20 & 32.56
%\end{tabular}
%\end{table}

%\subsection{With/without time delays and central image} %--------------------------------------------------------------

%We also considered the effect of having time delays or a central image. The
%central image is usually highly demagnified and obscured by the lensing galaxy,
%but in clusters the central image is observable. In this case we can imagine
%the galaxies to be clusters since the problem is scale-free. A recontruction of
%AASingleQuadR1a\_Tm is shown in \figref{AASingleQuadR1a_Tm}. The suffix denotes
%which combination of time delays (T) and central image (M) was used. An
%uppercase letter indicates the feature is turned on, and a lowercase letter
%that it is turned off.

%\begin{figure}
%\plotone{AASingleQuadR1a_Tm.png}
%\caption{The reconstruction of AASingleQuadR1a\_Tm.}
%\end{figure}

@@

\figref{AAZContrastR1R5_Tm reconstruction} shows a typical reconstruction of a
lens. The far left plot shows the arrival time surface with image marked as
circles and the inferred source position as a diamond. The center plot shows
the radial density profile. The error bars cover the full range of models
generated by \Glass. The true density profile from the mock data is also
plotted for comparison. The vertical lines mark the radial position of the
images. The final plot on the right is of the enclosed mass. As expected the
error bars are smallest in the region of the images where the most information
about the lens is present. The dip in the profile at the end of the profile
is due to the cut off in mass in the lensing map. This is of little importance,
though, as there is no lensing information there.

\begin{figure}
\plotone{AAZContrastR1R5_Tm.pdf}
\caption{A typical reconstructed lens. 
\textbf{(Left)}
The arrival time surface. In this case, there are two sources at different
redshifts with galaxy AA. The next three panels show the radial density,
average enclosed density, and enclosed mass profiles, respectively.  The grey
curve is from the galaxy and the vertical lines show the positions of the
images for the two sources.}
\label{AAZContrastR1R5_Tm reconstruction}
\end{figure}

\begin{figure}
\plotone{AAresults.pdf}
\end{figure}

%\subsection{Model quality}
We estimate the quality of a model $\M_i$ by comparing the recovered
density profile $\rho_\M(r)$ against the profile of the mock galaxy $\rho_G(r)$.
In particular, the plots show the RMS quantity
%
\begin{equation}
  \chi_i = 100 \times \sqrt{\frac{\int_r (\rho_{\M_i}(r) - \rho_G(r))^2}{\int_r \rho_G(r)^2}}
  %\chi_i = \frac{\sum_r (\rho(r)_{\M_i} - \rho(r)_G)^2}{\sum_r \rho(r)_G^2}
\end{equation}

\subsection{Using principle component analysis to find new degeneracies}

%\begin{figure}
%\label{chi2}
%\plottwo{AAchi2_profile.pdf}{AAchi2_profile.pdf} \\
%\plottwo{BBchi2_profile.pdf}{BCchi2_profile.pdf}
%\caption{
%Goodness of fit plots for the reconstruction of each of the four galaxies given
%the different lensing test cases. The $\chi^2$ is computed over the radial $\kappa$
%profile with data points at the median value and the error bars showing the 68\% confidence
%interval.
%}
%\end{figure}

@@

\subsection{Aperture}

\section{Discussion} %--------------------------------------------------------------

@@

@@

%\section{GLASS - An Extensible Gravitational Lens Modeling Framework}
%\label{GLASS Description}
%\begin{itemize} 
%\item Framework that incorporates lens modeling, analysis, and plotting.
%\item Not limited to just pixels based modeling. Can be used with functional forms like Bessel functions. Not yet implemented.
%\item Allows for post processing and criteria matching on a per model basis.
%\item Input files are python programs but from within the framework that aspect may be ignored.
%
%\item Lens reconstruction. Based on PixeLens. Express data constraints and
%priors as linear equations. Sample the resulting simplex.
%\item Standard data constraints: image positions, time delays, hubble constant, parity, annular density, external shear.
%\item Priors: range of profile steepness, local gradient, smoothness, shared H0, symmetry for doubles.
%\item Local gradient and smoothness are now convergent. Based on physical size rather than number of neighbors.
%
%\item Raytracing. Use a fine grid to sample the 2d function mapping position on
%the image plane to distance from the source on the source plane. From those
%points that are near the source, use a 2d root finder to locate the exact
%positions. Merge nearly identical solutions.

%\end{itemize}
